Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
similarly -> also

Planets with strong magnetic fields may generate radio and/or X-ray emission when interacting with energetic charged particles. 
It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
Exoplanets could similarly generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons.
This process could provide an avenue to discover planets that are otherwise extremely difficult to find --- those orbiting highly-evolved stars.
Unlike traditional methods of discovering exoplanets, in which the planetary signal is a tiny perturbation on light from the star, low-frequency planetary radio emission might be an arena where planets are vastly brighter than their stars.
This paper is an exploration of the surprisingly diverse range of physical processes that lead to this emission, and the prospects for detecting radio emission from planets around giant stars with current and near-future low-frequency radio observatories.

>>>>

Planets with strong magnetic fields may generate radio and/or X-ray emission when interacting with energetic charged particles. 
It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
Exoplanets could also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons.
This process could provide an avenue to discover planets that are otherwise extremely difficult to find --- those orbiting highly-evolved stars.
Unlike traditional methods of discovering exoplanets, in which the planetary signal is a tiny perturbation on light from the star, low-frequency planetary radio emission might be an arena where planets are vastly brighter than their stars.
This paper is an exploration of the surprisingly diverse range of physical processes that lead to this emission, and the prospects for detecting radio emission from planets around giant stars with current and near-future low-frequency radio observatories.
